Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-21 main.tex
Fix that N_0 was not defined (close #17)
Added subsection in Section 5 for better outline

The look ahead functionality seems to solve the problems for functions. But there is another problem that was not mentioned in \Cref{sec:problems}, because it seems to be not a problem previously. In some cases the arguments of a function do not follow but precede the function node.

@@

We have also noticed that our testing procedure is able to identify errors in CAS procedures,
namely the \Maple{} {\tt simplify} procedure. The left-hand side of~\parencite[(7.18.4)]{NIST:DLMF} is given by 
\begin{equation*}
\frac{{\mathrm{d}}^{n}}{{\mathrm{d}z}^{n}}\left(e^{z^{2}}\operatorname{erfc}z\right),
\end{equation*}
where $n \in \mathbb{N}_0$, $e$ is the base of the natural logarithm, and $\operatorname{erfc}$ is the
complementary error function. Our translation correctly produces 
\begin{equation*}
\verb|diff((exp((z)^(2))*erfc(z)), [z$(n))]|.
\end{equation*}
However, the \Maple{ 2016} \verb|simplify| function falsely returns $0$ for the translated left-hand side.
Maplesoft has confirmed in a private communication that this is indeed a defect in \Maple{ 2016}.
Furthermore, although the nature of the defect changes, the defect still persists in \Maple{ 2018}
as of the publication of this manuscript.

>>>>

\subsection{Problems with the Look Ahead Approach}
The look ahead functionality seems to solve the problems for functions. But there is another problem that was not mentioned in \Cref{sec:problems}, because it seems to be not a problem previously. In some cases the arguments of a function do not follow but precede the function node.

@@

We have also noticed that our testing procedure is able to identify errors in CAS procedures,
namely the \Maple{} {\tt simplify} procedure. The left-hand side of~\parencite[(7.18.4)]{NIST:DLMF} is given by 
\begin{equation*}
\frac{{\mathrm{d}}^{n}}{{\mathrm{d}z}^{n}}\left(e^{z^{2}}\operatorname{erfc}z\right), \quad n = {0,1,2,\ldots}
\end{equation*}
where $e$ is the base of the natural logarithm, and $\operatorname{erfc}$ is the
complementary error function. Our translation correctly produces 
\begin{equation*}
\verb|diff((exp((z)^(2))*erfc(z)), [z$(n))]|.
\end{equation*}
However, the \Maple{ 2016} \verb|simplify| function falsely returns $0$ for the translated left-hand side.
Maplesoft has confirmed in a private communication that this is indeed a defect in \Maple{ 2016}.
Furthermore, although the nature of the defect changes, the defect still persists in \Maple{ 2018}
as of the publication of this manuscript.
